A generic and fast C++ optimization framework

### 2017-10-21 paper.tex
Fix missing parentheses
Use two column style for the code snippets.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{minted}

@@

In addition to these function types, certain optimizers require specific
functionality to achieve their goal. The {\tt FunctionType} API offers users the
flexibility to define a custom function signature. As an example, {\bf mlpack}'s
implementation of L-BFGS requires a function that exposes a
{\tt GetInitialPoint} function.

@@

{\bf <TODO: add very simple example function>}

@@

\begin{minted}{c++}
class SparseFunction
{
  SparseFunction()
  {
    intercepts = arma::vec("20 12 15 100");
    bi = arma::vec("-4 -2 -3 -8");
  }

  double Evaluate(const arma::mat& p, const size_t i)
  {
    return p[i] * p[i] + bi[i] * p[i] + intercepts[i];
  }

  void Gradient(const arma::mat& p, const size_t i, arma::sp_mat& g)
  {
    g.zeros(arma::size(p));
    g[i] = 2 * p[i] + bi[i];
  }
}
\end{minted}

First, we would like to define {\tt Optimize()} which takes the function we like
to optimize and the function parameters as an Armadillo dense matrix type as
input.

\begin{minted}{c++}
template<typename FunctionType, typename ParameterType>
double Optimize(DecomposableFunctionType& function, ParameterType& parameter);
\end{minted}

Now, we can use {\tt Gradient()} to write a simple stochastic gradient descent
method with a static learning rate to optimize the function parameter.

\begin{minted}{c++}
for (size_t i = 0; i < 300; ++i)
{
  const size_t functionIndex = i % 4;
  function.Gradient(parameter, functionIndex, gradient);
  parameter -= 0.1 * gradient;
}
\end{minted}

Lastly, we would like to calculate the final objective. This can be done by
iterating over the parameter space using {\tt Evaluate()}.

\begin{minted}{c++}
double objective = 0;
for (size_t i = 0; i < 4; ++i)
  objective += function.Evaluate(parameter, i);
\end{minted}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{minted}
\usepackage{caption}
\usepackage{parcolumns}

@@

In addition to these function types, certain optimizers require specific
functionality to achieve their goal. The {\tt FunctionType} API offers users the
flexibility to define a custom function signature. As an example, {\bf mlpack}'s
implementation of L-BFGS requires a function that exposes a
{\tt GetInitialPoint()} function.

@@

@@

\begin{figure}[H]
\begin{minipage}[t]{0.49\textwidth}
\centering
\begin{minted}[fontsize=\footnotesize]{c++}
class ObjectiveFunction {
 ObjectiveFunction() {
  in = arma::vec(
    "20 12 15 100");
  bi = arma::vec("-4 -2 -3 -8");
 }

 void Shuffel() {
  order = arma::shuffle(
   arma::linspace<arma::uvec>(0, 3, 4));
 }

 size_t NumFunctions() { return 4; }

 double Evaluate(const arma::mat& p,
  size_t s, size_t b) {
  double cost = 0;
  for (size_t i = s; i < s + b; i++) {
   cost += std::pow(p(i), 2) +
    bi(order(i)) * p(order(i)) +
    in(order(i));
  }
  return cost;
 }

 void Gradient(const arma::mat& p,
  size_t s, size_t b, arma::sp_mat& g) {
  g.zeros(arma::size(p));

  for (size_t i = s; i < s + b; i++) {
   g(i) += 2 * p(i) + bi(order(i));
 }
}
\end{minted}
\vspace{2\baselineskip}
% \captionof{listing}{Distinct parabola sparse function.}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
\centering
\begin{minted}[fontsize=\footnotesize]{c++}
class ObjectiveFunction {
 ObjectiveFunction() {
  in = arma::vec(
    "20 12 15 100");
  bi = arma::vec("-4 -2 -3 -8");
 }

 void Shuffel() {
  order = arma::shuffle(
   arma::linspace<arma::uvec>(0, 3, 4));
 }

 size_t NumFunctions() { return 4; }

 double Evaluate(const arma::mat& p,
  size_t s, size_t b) {
  double cost = 0;
  for (size_t i = s; i < s + b; i++) {
   cost += std::pow(p(i), 2) +
    bi(order(i)) * p(order(i)) +
    in(order(i));
  }
  return cost;
 }

 void Gradient(const arma::mat& p,
  size_t s, size_t b, arma::sp_mat& g) {
  g.zeros(arma::size(p));

  for (size_t i = s; i < s + b; i++) {
   g(i) += 2 * p(i) + bi(order(i));
 }
}
\end{minted}
% \captionof{listing}{Optimizer class.}
\end{minipage}
\captionof{listing}{not relevant}
\end{figure}
